>

### 2020-05-13 manuscript/manuscript.Rmd
Initial responses to some reviewer comments

We calculate a pair of utility-based accessibility statistics for each tract
in New York City. The most basic utility specification includes only the
park size in acres and the distance from the population-weighted tract centroid
to the boundary of the park in miles,
\begin{equation}\label{eq:u_access}
V_{ij} = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij})
\end{equation}
The logarithmic transform allows for diminishing marginal utility of distance
and park size: A 1-mile increase to a trip matters more for a 1-mile trip than a
10-mile trip. @Macfarlane2019 estimated destination choice 
parameters for park trips in Alameda County (Oakland), California by applying
this utility specification to passively collected mobile device data, obtaining values of $\lambda_s = 0.373$ and 
$\lambda_d = -1.76$. The ratio of these estimates implies people are willing to
travel roughly six times further to reach a park twice as large. We do not have
access to the necessary data to repeat the @Macfarlane2019 methodology in New
York, and the public parks datasets in Alameda County are
not sufficiently detailed to perform the present accessibility analysis there.
In the absence of park trip destination choice coefficients in New York City, we
adopt these previous estimates.

@@

We predict either the physical activity or the obesity rate ($y$) in a census
tract as a linear function of the tract's sociodemographic characteristics $X$
and accessibility to parks $A$,
\begin{equation}\label{eq:themodel}
 \boldsymbol{y} = X\boldsymbol{\beta} + \beta_{a}\boldsymbol{A} + \boldsymbol{\varepsilon}
\end{equation}

@@

Note that in the lag-$X$ specifications (SLX and SDEM) we exclude the accessiblity 
component $A$, that is we do *not* consider that the accessibility
in a neighboring zone will have an effect on physical activity or obesity rates.
In a practical sense, this is because the accessibility term $A$ is itself spatially
determined.

@@

As far as the accessibility values are concerned, none of the three
utility-based specifications nor the ParkScore 10-minute walk buffer are
correlated with obesity rates at the traditional 95\% confidence interval. 
It is important to consider the implications of the full range of the confidence
interval, however [@Amrhein2019]. The results suggest that after controlling
for tract socioeconomic variables, physical activity rates, and spatially correlated
error terms, obesity rates in tracts with excellent park accessibility are expected 
to be between `r 6 * 0.113` percentage points lower and `r 6 * .0425` percentage 
points higher than tracts with poor park accessibility. This range of values 
suggests that accessibility to parks may have obesity-reducing effects beyond
the effect of accessibility on physical activity rates worth further study.

@@

This paper applies a previously-presented but little-used accessibility
statistic that could, in theory, accommodate many attributes of the destination
parks as well as the people who might use them. As an illustration: the
park-going population could be separated into at least four delineated clusters,
each preferring different amenities of a park:
\begin{itemize}
 \item{runners and cyclists: long, interesting trail systems}
 \item{sports players: soccer fields, basketball courts, or baseball diamonds}
 \item{families with small children: water features and playgrounds}
 \item{casual users: water features, gardens, performances, etc.}
\end{itemize}
An analyst could then compute the utility-based accessibility for each cluster
with different utility values for each park's amenities, and obtain a measure of
a neighborhood's accessibility to park features that its residents most care
about. In this paper, we proceed only incrementally towards this by adding some
selected park amenities as an element of each park's
attractiveness above and beyond its size. Exploring detailed definitions of
an increased number of amenities on one hand, and market segmentation strategies
on the other, could provide a more nuanced understanding of the relationship
between park accessibility and health outcomes.

As a travel impedance measure, we used the Euclidean distance between each tract's
population-weighted centroid and the nearest point on the edge of a park's border.
Euclidean distances have well-rehearsed limitations regarding their fidelity with
the underlying infrastructure network, etc. Network-based distances can also
suffer from challenges when applied to multimodal problems; these challenges are
exacerbated when the non-highway mode share is high, as is likely when considering
access to parks. A better metric of travel impedance may be a mode choice model
logsum, which weights all alternative travel alternatives against each other. 
We leave this as a recommendation for future research.

>>>>

We calculate a pair of utility-based accessibility statistics for each tract
in New York City. The most basic utility specification includes only the
park size in acres and the Euclidean distance from the population-weighted tract
centroid to the nearest boundary of the park in miles,
\begin{equation}\label{eq:u_access}
V_{ij} = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij})
\end{equation}
There are a few cases where the population-weighted tract centroid lies on or
within the boundary of a park; for these cases we assert that the minimum
possible distance is one tenth of a mile.
The logarithmic transform allows for diminishing marginal utility of distance
and park size: A 1-mile increase to a trip matters more for a 1-mile trip than a
10-mile trip. @Macfarlane2019 estimated destination choice 
parameters for park trips in Alameda County (Oakland), California by applying
this utility specification to passively collected mobile device data, obtaining values of $\lambda_s = 0.373$ and 
$\lambda_d = -1.76$. The ratio of these estimates implies people are willing to
travel roughly six times further to reach a park twice as large. We do not have
access to the necessary data to repeat the @Macfarlane2019 methodology in New
York, and the public parks datasets in Alameda County are
not sufficiently detailed to perform the present accessibility analysis there.
In the absence of park trip destination choice coefficients in New York City, we
adopt these previous estimates.

@@

We predict either the physical activity or the obesity rate ($y$) in a census
tract as a linear function of the tract's sociodemographic characteristics $X$
and accessibility to parks $\boldsymbol{A}$,
\begin{equation}\label{eq:themodel}
 \boldsymbol{y} = X\boldsymbol{\beta} + \beta_{a}\boldsymbol{A} + \boldsymbol{\varepsilon}
\end{equation}
where $X$ is a matrix of dimension $n\times p$ where $n$ is the number of observations and $p$ is the number of predictor
variables, and $\boldsymbol{\beta}$ is a $p\times 1$ vector of estimated parameters.
The accessibility vector $\boldsymbol{A}$ influences physical activity or obesity rates by the
single estimated parameter $\beta_a$, and a vector $\boldsymbol{\varepsilon}$ 
represents the model residual as a random variable.

@@

Note that in the lag-$X$ specifications (SLX and SDEM) we exclude the accessiblity 
component $\boldsymbol{A}$, that is we do *not* consider that the accessibility
in a neighboring zone will have an effect on physical activity or obesity rates.
In a practical sense, this is because the accessibility term $\boldsymbol{A}$ is itself spatially
determined.

@@

As far as the accessibility values are concerned, none of the three
utility-based specifications nor the ParkScore 10-minute walk buffer are
correlated with obesity rates at the traditional 95\% confidence interval. 
It is important to consider the implications of the full range of the confidence
interval, however [@Amrhein2019]. The results suggest that after controlling
for tract socioeconomic variables, physical activity rates, and spatially correlated
error terms, obesity rates in tracts with excellent park accessibility are expected 
to be between `r 6 * 0.12` percentage points lower and `r 6 * .035` percentage 
points higher than tracts with poor park accessibility. This range of values 
suggests that accessibility to parks may have obesity-reducing effects beyond
the effect of accessibility on physical activity rates worth further study.

@@

This paper applies a previously-presented but little-used accessibility
statistic that could, in theory, accommodate many attributes of the destination
parks as well as the people who might use them. As an illustration: the
park-going population could be separated into at least four delineated clusters,
each preferring different amenities of a park:
\begin{itemize}
 \item{runners and cyclists: long, interesting trail systems}
 \item{sports players: soccer fields, basketball courts, or baseball diamonds}
 \item{families with small children: water features and playgrounds}
 \item{casual users: water features, gardens, performances, etc.}
\end{itemize}
An analyst could then compute the utility-based accessibility for each cluster
with different utility values for each park's amenities, and obtain a measure of
a neighborhood's accessibility to park features that its residents most care
about. In this paper, we proceed only incrementally towards
this by adding some selected park amenities as an element of each park's
attractiveness above and beyond its size. The set of amenities we included in
the utility calculation --- and the contribution of each amenity to the overall
utility --- was dictated by the availability of data on the park amenities in New
York City and our ability to find comparable prior studies with transferrable
utility parameters. We can envision a study where mobile device data
revealing the home locations of park users would be paired with more detailed
park amenities and use data (e.g. geolocated Twitter data *a la*
@roberts2017using) to estimate the utility contribution of these features. This
could in turn provide a more nuanced understanding of the relationship between
park accessibility, use, and health outcomes.

As a travel impedance measure, we used the Euclidean distance between each tract's
population-weighted centroid and the nearest point on the edge of a park's border.
Euclidean distances have well-rehearsed limitations regarding their fidelity with
the underlying infrastructure network, etc. Network-based distances can also
suffer from challenges when applied to multimodal problems; these challenges are
exacerbated when the non-highway mode share is high, as is likely when considering
access to parks. We examined replacing the Euclidean distance with a network-based
distance; the choice of distance metric appeared inconsequential to our larger
findings in this case. We retained the Euclidean distance for computational simplicity. A
better metric of travel impedance may be a mode choice model logsum, which
weights all alternative travel alternatives against each other. We leave this as
a recommendation for future research.
